Scalar_M1

### 2015-05-11 models/Model_Playspace.Rmd
Minor tweaks to working dir call and priors plot. Need to fix RUN MODEL section

```{r}
rm(list=ls())
p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
source(paste0(p,"analysis/useful_dplyr.R"))
library(rjson)
```

@@

Priors
```{r}
qplot(c(1:5), raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Priors over ratings")
```

>>>>

```{r}
rm(list=ls())
#p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(rjson)
```

@@

Priors
```{r}
qplot(c(1:5), priors$prior.p,
      geom="bar", stat = "identity",
      binwidth = 1, main="Priors over ratings")
```
